Are parental care induced gene expression patterns affect more by internal cues or external stimuli?

### 2019-09-06 docs/manipulation_manuscript.Rmd
need more resutls

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
library(cowplot)
ggdraw() + draw_image("../figures/manipulation/offspringremoval-1.png") 
```

>>>>

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
ggdraw() + draw_image("../figures/manipulation/offspringremoval-1.png") 
```

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
ggdraw() + draw_image("../figures/manipulation/manipVchar-1.png") 
```

```{r, message=FALSE, warning=FALSE, cache=TRUE, echo = F, fig.width= 5}
ggdraw() + draw_image("../figures/manipulation/prolongextend-1.png") 
```
